Supplementary informations to Hierarchical wrinkling in a confined permeable biogel

### 2015-07-22 fig_plis/supplementary_plis.tex
Modifs Seb American English

\begin{document}
\title{Supplementary informations to Hierarchical wrinkling in a confined permeable biogel}
\author{Mathieu Leocmach}
\affiliation{Universit\'e de Lyon, Laboratoire de Physique, \'Ecole Normale Sup\'erieure de Lyon, CNRS UMR 5672, 46 All\'ee d'Italie, 69364 Lyon cedex 07, France}
\author{Mathieu Nespoulous}
\affiliation{Aix-Marseille Université, CNRS, MADIREL UMR 7246, Marseille, France}
\author{Sébastien Manneville}
\affiliation{Universit\'e de Lyon, Laboratoire de Physique, \'Ecole Normale Sup\'erieure de Lyon, CNRS UMR 5672, 46 All\'ee d'Italie, 69364 Lyon cedex 07, France}
\author{Thomas Gibaud}
\email{thomas.gibaud@ens-lyon.fr}
\affiliation{Universit\'e de Lyon, Laboratoire de Physique, \'Ecole Normale Sup\'erieure de Lyon, CNRS UMR 5672, 46 All\'ee d'Italie, 69364 Lyon cedex 07, France}

@@

Figure~\ref{fig:generations} shows Fourier spectra of binarised altitudes at different times. When only the first generation pattern is present a peak clearly indicates the dominant mode. When the secondary pattern has appeared, the dominant wavelength is halved and the peak much weaker. This allows us to use the secondary pattern is our analysis by setting their wavelength to half of the primary wavelength. Further generations do not seem to appear simultaneously and the corresponding peaks are weak and broad.

@@

The fraction of free casein proteins of a \SI{100}{\milli\litre}, 4\%w sodium caseinate dispersion is obtained either by titration by 1 molar HCl, see Supplementary Video~\ref{vid:titration}, or during the action of 4\%w GDL. In both cases, \SI{0.4}{\milli\litre} of the \SI{100}{\milli\litre} dispersion is sampled regularly as a function of pH, and centrifuged (centrifuge 5424, Eppendorf) in Eppendorf tubes at 14500 rpm for \SI{3}{\minute}. The supernatant is diluted and analysed with a UV absorption spectrometer (USB4000, Ocean Optics). According to~\cite{Roefs1986}, we deduce the fraction of free casein proteins from the adsorption spectrum as:
%
\begin{align}
x_\text{free} &= \frac{A(\text{pH})}{A(\text{pH}=7)},\\
\text{with }A(\text{pH}) &= A_{280}-1.706 A_{320},
\end{align}
%
where $A_{280}$ is the absorption peak at \SI{280}{\nano\metre} due to aromatic amino acids in the casein molecules plus a turbidity background whereas the absorption peak at \SI{320}{\nano\metre} is only due to turbidity.

@@

By fitting $z(t)-z_\infty$ to an exponential, see Supplementary Figure~\ref{fig:permeability} b-c, we obtain $\tau$ and thus $\alpha$. Note that even with $H$ of the order of a few millimetres high glycerol contents yield $\tau\approx \SI{100}{\hour}$ due to both high viscosity and low permeability. Obtaining $z_\infty$ without tube 2 would be time prohibitive.

@@

Combining equations~(\ref{eq:mecheqop}) and (\ref{eq:DarcyLoad}), the compression load writes
\begin{equation}
\sigma_\parallel = \frac{1}{12}B h^2 q^2 + \frac{\eta}{\tau}\frac{1}{\alpha q^2}
\label{eq:sigma0D}
\end{equation}
and is minimised at $q_D$ such that
\begin{equation}
q_D^4 = \frac{12}{h^2\alpha\Upsilon}.
\label{eq:qD}
\end{equation}
%
The dominant wavelength for Darcy model is thus
\begin{equation}
\lambda_D = 2\pi h^{1/2}\alpha^{1/4}\left(\frac{\Upsilon}{12}\right)^{1/4}.
\end{equation}
Here also the dominant mode maximises the growth rate.

>>>>

\begin{document}
\title{Supplementary informations to Hierarchical wrinkling in a confined permeable biogel}
\author{Mathieu Leocmach}
\affiliation{Universit\'e de Lyon, Laboratoire de Physique, \'Ecole Normale Sup\'erieure de Lyon, CNRS UMR 5672, 46 All\'ee d'Italie, 69364 Lyon cedex 07, France}
\author{Mathieu Nespoulous}
\affiliation{Aix-Marseille Universit\'e, CNRS, MADIREL UMR 7246, Marseille, France}
\author{S\'ebastien Manneville}
\affiliation{Universit\'e de Lyon, Laboratoire de Physique, \'Ecole Normale Sup\'erieure de Lyon, CNRS UMR 5672, 46 All\'ee d'Italie, 69364 Lyon cedex 07, France}
\author{Thomas Gibaud}
\email{thomas.gibaud@ens-lyon.fr}
\affiliation{Universit\'e de Lyon, Laboratoire de Physique, \'Ecole Normale Sup\'erieure de Lyon, CNRS UMR 5672, 46 All\'ee d'Italie, 69364 Lyon cedex 07, France}

@@

Figure~\ref{fig:generations} shows Fourier spectra of binarized altitudes at different times. When only the first generation pattern is present a peak clearly indicates the dominant mode. When the secondary pattern has appeared, the dominant wavelength is halved and the peak much weaker. This allows us to use the secondary pattern is our analysis by setting their wavelength to half of the primary wavelength. Further generations do not seem to appear simultaneously and the corresponding peaks are weak and broad.

@@

The fraction of free casein proteins of a \SI{100}{\milli\litre}, 4\%w sodium caseinate dispersion is obtained either by titration by 1 molar HCl, see Supplementary Video~\ref{vid:titration}, or during the action of 4\%w GDL. In both cases, \SI{0.4}{\milli\litre} of the \SI{100}{\milli\litre} dispersion is sampled regularly as a function of pH, and centrifuged (centrifuge 5424, Eppendorf) in Eppendorf tubes at 14500 rpm for \SI{3}{\minute}. The supernatant is diluted and analyzed with a UV absorption spectrometer (USB4000, Ocean Optics). According to~\cite{Roefs1986}, we deduce the fraction of free casein proteins from the adsorption spectrum as:
%
\begin{align}
x_\text{free} &= \frac{A(\text{pH})}{A(\text{pH}=7)},\\
\text{with }A(\text{pH}) &= A_{280}-1.706 A_{320},
\end{align}
%
where $A_{280}$ is the absorption peak at \SI{280}{\nano\metre} due to aromatic amino acids in the casein molecules plus a turbidity background whereas the absorption peak at \SI{320}{\nano\metre} is only due to turbidity.

@@

By fitting $z(t)-z_\infty$ to an exponential, see Supplementary Figure~\ref{fig:permeability} b-c, we obtain $\tau$ and thus $\alpha$. Note that even with $H$ of the order of a few millimeters high glycerol contents yield $\tau\approx \SI{100}{\hour}$ due to both high viscosity and low permeability. Obtaining $z_\infty$ without tube 2 would be time prohibitive.

@@

Combining equations~(\ref{eq:mecheqop}) and (\ref{eq:DarcyLoad}), the compression load writes
\begin{equation}
\sigma_\parallel = \frac{1}{12}B h^2 q^2 + \frac{\eta}{\tau}\frac{1}{\alpha q^2}
\label{eq:sigma0D}
\end{equation}
and is minimised at $q_D$ such that
\begin{equation}
q_D^4 = \frac{12}{h^2\alpha\Upsilon}.
\label{eq:qD}
\end{equation}
%
The dominant wavelength for Darcy model is thus
\begin{equation}
\lambda_D = 2\pi h^{1/2}\alpha^{1/4}\left(\frac{\Upsilon}{12}\right)^{1/4}.
\end{equation}
Here also the dominant mode maximizes the growth rate.
